Domain-agnostic Outlier Ranking Algorithms (DORA)---A Configurable Pipeline for Facilitating Outlier Detection in Scientific Datasets

### 2021-09-18 publications/iaai21/dora_outlier_detection_iaai.tex
Add discussion of overall algorithm performance. #42

For the astrophysics dataset (Figure~\ref{fig:des_results}, DEMUD was omitted due to computational time 
and LRX was omitted as it applies only to image data.  Of the remaining methods, 
PCA achieved the highest precision, following by RX.  Negative sampling 
performs well initially before its performance drops off.  The PAE finds the most outliers 
overall.

@@

\paragraph{Algorithm performance.} \todo{Discuss overall results from
 experiments and that we left hyperparameter tuning and extensive
 evaluation for future work.}

>>>>

For the astrophysics dataset (Figure~\ref{fig:des_results}), DEMUD was omitted due to computational time 
and LRX was omitted as it applies only to image data.  Of the remaining methods, 
PCA achieved the highest precision, following by RX.  Negative sampling 
performs well initially before its performance drops off.  The PAE finds the most outliers 
overall.

@@

\paragraph{Algorithm performance.} There was no one algorithm that 
consistently had the best performance across all four datasets. PCA had
the best performance overall for the astrophysics and F-MNIST datasets, 
while negative sampling and isolation forest had the best performance for
the Earth science and planetary datasets respectively. [This shows why
it is best for us to include a variety of algorithms because the best 
algorithm will vary depending on the dataset.] The purpose of this study
was to demonstrate how DORA could be used to facilitate comprehensive
outlier detection experiments and compare results across datasets from 
different domains. Thus we chose hyperparameters based on common 
practice and sense and leave hyperparameter tuning, which would likely 
improve results for each dataset but would require
creation of additional validation sets, for future work.
